Approximation as Differentiation

### 2025-05-04 appendix/notes/grothendieck.tex
Homing in on chain rule in Grothendieck construction.

\begin{definition}[Grothendieck construction for $F$]
Suppose an indexed category $T: \cat{C}^\op \to \Cat$. The \emph{Grothendieck construction}
for $T$ is the category $\Grothendieck{}T$ which has:
\begin{itemize}
\item as objects, all pairs $(X, \partial X)$ of an object $X$ of $\cat{C}$ and an object $\partial X$ of $F(X)$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$ all pairs $(f, \partial f)$ of morphisms $f: X
\to Y$ in $\cat{C}$ and morphisms $\partial f: \partial X \to F(Y)(\partial Y)$ in $F(X)$.
\end{itemize}
\end{definition}

>>>>

\begin{definition}[Grothendieck construction for $F$]
Suppose an indexed category $T: \cat{C}^\op \to \Cat$. The \emph{Grothendieck construction}
for $T$ is the category $\Grothendieck{}T$ which has:
\begin{itemize}
\item as objects, all pairs $(X, \partial X)$ of an object $X$ of $\cat{C}$ and an object $\partial X$ of
$T(X)$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs $(f, \partial f)$ of morphisms $f: X \to
Y$ in $\cat{C}$ and morphisms $\partial f: \partial X \to T(f)(\partial Y)$ in $T(X)$.
\end{itemize}
\end{definition}

For any $(f, \partial f): (X, \partial X) \to (Y, \partial Y)$ and $(g, \partial g): (Y, \partial Y)
\to (Z, \partial Z)$ in $\Grothendieck{}T$, we have:

\begin{itemize}
\item $\partial f: \partial X \to T(f)(\partial Y)$;
\item $T(f)(\partial g): T(f)(\partial Y) \to T(f)(T(g)(\partial Z)) = T(g \comp f)(\partial Z)$.
\end{itemize}

\noindent The composition $(g, \partial g) \comp (f, \partial f): (X, \partial X) \to (Z, \partial Z)$ is
given by $(g \comp f, T(f)(\partial g) \comp \partial f)$.
